\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex

For each of these scenarios, our greedy heuristic got the exact same answer as the
brute-force algorithm as well as the intuitive solution from the graph. Because our greedy heuristic found the same answer as the brute-force algorithm (which looked for the ideal, optimal answer) our greedy heuristic seems to be performing extremely efficiently and accurately.

>>>>

For each of these scenarios, our greedy heuristic got the exact same answer as the
brute-force algorithm as well as the intuitive solution from the graph. Because our greedy heuristic found the same answer as the brute-force algorithm (which looked for the ideal, optimal answer) our greedy heuristic seems to be performing efficiently and accurately.
